Appendix: Trends in age-adjusted mortality rates for blacks and whites by cause and sex, 1969-2013, United States

### 2017-02-28 Code/combine_results.Rmd
updated with all states

completed.states <- included.states[c(1:11, 14, 17:24, 26:27, 33:34)]
```

@@

```{r add_Census_Variables, echo = F}
BlackWhite_results <- add_Census_Region(BlackWhite_results, state)
BlackWhite_results <- add_Census_Division(BlackWhite_results, state)
BlackWhite_results$stabbrs <- state.abb[match(BlackWhite_results$state, state.name)]

>>>>

completed.states <- included.states
```

@@

```{r add_Census_Variables, echo = F}
BlackWhite_results <- add_Census_Region(BlackWhite_results, state)
BlackWhite_results <- add_Census_Division(BlackWhite_results, state)
BlackWhite_results$stabbrs <- state.abb[match(BlackWhite_results$state, state.name)]
BlackWhite_results$stabbrs[BlackWhite_results$state == "Washington DC"] <- "DC"

### 2017-02-28 Manuscript/Appendix-agestd-mort-rates.Rmd

# Create unique blank strip labels for empty facets
bl = sapply(1:38, function(n) paste(rep(" ",n),collapse=""))

mortality.rates$state.reorder2 <- factor(mortality.rates$state,
                                        levels = c(bl[1:10], "Maine",
                                                   bl[11:19], "Vermont", "New Hampshire",
                                                   "Washington", "Idaho", "Montana", "North Dakota", "Minnesota", "Illinois", "Wisconsin", "Michigan", "New York", "Massachusetts", "Rhode Island",
                                                   "Oregon", "Nevada", "Wyoming", "South Dakota", "Iowa", "Indiana", "Ohio", "Pennsylvania", "New Jersey", "Connecticut", bl[20],
                                                   "California", "Utah", "Colorado", "Nebraska", "Missouri", "Kentucky", "West Virginia", "Virginia", "Maryland", "Washington DC", bl[21],
                                                   bl[22], "Arizona", "New Mexico", "Kansas", "Arkansas", "Tennessee", "North Carolina", "South Carolina", "Delaware", bl[23:24],
                                                   bl[25:27], "Oklahoma", "Louisiana", "Mississippi", "Alabama", "Georgia", bl[28:29],
                                                   bl[30:33], "Texas", bl[34:38], "Florida"))

mortality.rates.diff$state.reorder2 <- factor(mortality.rates.diff$state,
                                        levels = c(bl[1:10], "Maine",
                                                   bl[11:19], "Vermont", "New Hampshire",
                                                   "Washington", "Idaho", "Montana", "North Dakota", "Minnesota", "Illinois", "Wisconsin", "Michigan", "New York", "Massachusetts", "Rhode Island",
                                                   "Oregon", "Nevada", "Wyoming", "South Dakota", "Iowa", "Indiana", "Ohio", "Pennsylvania", "New Jersey", "Connecticut", bl[20],
                                                   "California", "Utah", "Colorado", "Nebraska", "Missouri", "Kentucky", "West Virginia", "Virginia", "Maryland", "Washington DC", bl[21],
                                                   bl[22], "Arizona", "New Mexico", "Kansas", "Arkansas", "Tennessee", "North Carolina", "South Carolina", "Delaware", bl[23:24],
                                                   bl[25:27], "Oklahoma", "Louisiana", "Mississippi", "Alabama", "Georgia", bl[28:29],
                                                   bl[30:33], "Texas", bl[34:38], "Florida"))
```

>>>>

# Create unique blank strip labels for empty facets
bl = sapply(1:37, function(n) paste(rep(" ",n),collapse=""))

mortality.rates$state.reorder2 <- factor(mortality.rates$state,
                                        levels = c(bl[1:10], "Maine",
                                                   bl[11:19], "Vermont", "New Hampshire",
                                                   "Washington", "Idaho", "Montana", "North Dakota", "Minnesota", "Illinois", "Wisconsin", "Michigan", "New York", "Massachusetts", "Rhode Island",
                                                   "Oregon", "Nevada", "Wyoming", "South Dakota", "Iowa", "Indiana", "Ohio", "Pennsylvania", "New Jersey", "Connecticut", bl[20],
                                                   "California", "Utah", "Colorado", "Nebraska", "Missouri", "Kentucky", "West Virginia", "Virginia", "Maryland", "Delaware", bl[21],
                                                   bl[22], "Arizona", "New Mexico", "Kansas", "Arkansas", "Tennessee", "North Carolina", "South Carolina", "Washington DC", bl[23:24],
                                                   bl[25:27], "Oklahoma", "Louisiana", "Mississippi", "Alabama", "Georgia", bl[28:29],
                                                   bl[30:33], "Texas", bl[34:37], "Florida"))

mortality.rates.diff$state.reorder2 <- factor(mortality.rates.diff$state,
                                        levels = c(bl[1:10], "Maine",
                                                   bl[11:19], "Vermont", "New Hampshire",
                                                   "Washington", "Idaho", "Montana", "North Dakota", "Minnesota", "Illinois", "Wisconsin", "Michigan", "New York", "Massachusetts", "Rhode Island",
                                                   "Oregon", "Nevada", "Wyoming", "South Dakota", "Iowa", "Indiana", "Ohio", "Pennsylvania", "New Jersey", "Connecticut", bl[20],
                                                   "California", "Utah", "Colorado", "Nebraska", "Missouri", "Kentucky", "West Virginia", "Virginia", "Maryland", "Delaware", bl[21],
                                                   bl[22], "Arizona", "New Mexico", "Kansas", "Arkansas", "Tennessee", "North Carolina", "South Carolina", "Washington DC", bl[23:24],
                                                   bl[25:27], "Oklahoma", "Louisiana", "Mississippi", "Alabama", "Georgia", bl[28:29],
                                                   bl[30:33], "Texas", bl[34:37], "Florida"))
```
